Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-14 paper/paper.Rmd
small change to image char
Latex table edits

*** (1) Check caption sentences finish with "." (2) Check spelling (3) Check no referring to tables and figures in the text like "the table below ..." or the "figure above ..." (4) Check all the writing is in third person, remove "We then ..." (5) One sentence paragraphs should be very rarely used, and I suspect there are too many in the current draft. Check if the orphan sentence better belongs with the prior or after paragraph.

@@

# letter value plots
t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
  geom_lv(aes(fill = ..LV..)) +
  #ylim(c(0, 0.1)) + 
  facet_wrap(~type) +
  scale_y_continuous("System time (ms)", 
    breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
  # somethings funky when try to change axis labels
  xlab("Number of faces detected")

@@

AM <- table(FacesAPI$Manual, FacesAPI$Animetrics, dnn = c("Manual", "Animetrics"))
GM <- table(FacesAPI$Manual, FacesAPI$Google, dnn = c("Manual", "Google"))
MM <- table(FacesAPI$Manual, FacesAPI$Microsoft, dnn = c("Manual", "Microsoft"))
SM <- table(FacesAPI$Manual, FacesAPI$Skybiometry, dnn = c("Manual", "Skybiometry"))
```

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Contingency tables of each API capture against manual tagging. Interestingly all APIs reported faces that would not be considered faces by manual inspection.}
\label{tab:facecounts}
\centering
\begin{tabular}{ccccccc} \cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 434 & 1861 & & Face & 1319 & 976\\
No Face &527 & 787 & & No Face &638 & 676 \\\cline{1-3}\cline{5-7}
\end{tabular}
\\[1.5ex]
\begin{tabular}{ccccccc}\\\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\
\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 565 & 1730 & & Face & 493 & 1802\\
No Face &505 & 809 & & No Face &512 & 802 \\\cline{1-3}\cline{5-7}
\end{tabular}
\end{table}

*** I've decided that these should be proportions.

@@

prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)

@@

glassesdf <- rbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
c("No", 
  round(glassesTab[1,2]/glassesTab[1,1],2),
  round(glassesTab[1,3]/glassesTab[1,1],2),
  round(glassesTab[1,4]/glassesTab[1,1],2),
  round(glassesTab[1,5]/glassesTab[1,1],2)),
c("Yes", 
  round(glassesTab[2,2]/glassesTab[2,1],2),
  round(glassesTab[2,3]/glassesTab[2,1],2),
  round(glassesTab[2,4]/glassesTab[2,1],2),
  round(glassesTab[2,5]/glassesTab[2,1],2)))

pander(glassesdf, caption = "Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces. API's unaffected glasses will have similar proportions for both categories. Animetrics had the biggest proportion difference, and thus, most affected. Google is the least affected.")
```

>>>>

@@

# letter value plots
t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
  geom_lv(aes(fill = ..LV..)) +
  #ylim(c(0, 0.1)) + 
  facet_wrap(~type) +
  scale_y_continuous("System time (seconds)", 
    breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
  # somethings funky when try to change axis labels
  xlab("Number of faces detected")

@@

GM <- CrossTable(FacesAPI$Manual, FacesAPI$Google)
MM <- CrossTable(FacesAPI$Manual, FacesAPI$Microsoft)
SM <- CrossTable(FacesAPI$Manual, FacesAPI$Skybiometry)
AM <- CrossTable(FacesAPI$Manual, FacesAPI$Animetrics)
```

\begin{table}[htp]
\centering
\caption{Table of the amount and proportion of faces each API captured, by manual tagging.}
\label{tab:facecounts}
\begin{tabular}{lllll}\\\cline{1-5}
            & \multicolumn{2}{l}{Faces found} & \multicolumn{2}{l}{Non-faces detected as faces} \\\cline{1-5}

            & Count        & Proportion       & Count                & Proportion               \\\cline{1-5}
Google      & 1319         & 0.57             & 638                  & 0.49                     \\
Microsoft   & 565          & 0.24             & 505                  & 0.38                     \\
Skybiometry & 493          & 0.22             & 512                  & 0.39                     \\
Animetrics  & 434          & 0.19             & 527                  & 0.40\\ \cline{1-5}
\end{tabular}
\end{table}

@@

#prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
```

@@

glassesdf <- rbind(c(" ", "Animetrics","Google","Microsoft","Skybiometry"),
c("No", 
  round(glassesTab[1,2]/glassesTab[1,1],2),
  round(glassesTab[1,3]/glassesTab[1,1],2),
  round(glassesTab[1,4]/glassesTab[1,1],2),
  round(glassesTab[1,5]/glassesTab[1,1],2)),
c("Yes", 
  round(glassesTab[2,2]/glassesTab[2,1],2),
  round(glassesTab[2,3]/glassesTab[2,1],2),
  round(glassesTab[2,4]/glassesTab[2,1],2),
  round(glassesTab[2,5]/glassesTab[2,1],2)))
```

\begin{table}[ht]
\centering
%\parbox{.5\linewidth}{
\caption{Conditional proportions of faces of players wearing glasses or not, captured by the different software, in comparison to the manually tagged faces. API's unaffected glasses will have similar proportions for both categories. Animetrics had the biggest proportion difference, and thus, most affected. Google is the least affected.} 
\label{tab:glasses}
\begin{tabular}{ccccc}
\hline 
 & Animetrics & Google & Microsoft & Skybiometry\\ 
\hline
Glasses & 0.08 & 0.43 & 0.14 & 0.12 \\
No Glasses & 0.21 & 0.60 & 0.26 & 0.23\\
\hline
\end{tabular}
\end{table}
